---
title: "Datatable preparation script for eDNA metabarcoding - Stellwagen Bank National Marine Sanctuary 2021 data"
output:
  github_document: default
  pdf_document:
    keep_tex: yes
  html_document:
    toc: yes
    toc_depth: 6
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---

This script takes your Blast output from the GMGI database, Mitofish database, and NCBI database to create one datatable with read counts and taxonomic assignment.  


# Load libraries

```{r}
library(ggplot2) ## for plotting
library(dplyr) ## for data table manipulation
library(tidyr) ## for data table manipulation
library(readr) ## for reading in tsv files
library(readxl) ## for reading in excel files
library(stringr) ## for data transformation
library(strex) ## for data transformation
library(writexl) ## for excel output
library(purrr) ## for data transformation
library(funrar) ## for make_relative()
library(tidyverse) ## for data transformation
```

# Metadata input

## Identify paths for metadata and project data 

Each user needs to write in their specific directory outputs prior to the file name. The default working directory is this document so the folder where this script is saved for the user. To change the workign directory to the Rproject directory, select 'Knit' and 'Knit Directory' > 'Project Directory'.

```{r}
### User edits:
### 1. change paths of input and output as desired 

## GMGI Fish database
path_GMGIdb = "../../Metabarcoding Lab Resources/Reference Databases/GMGI_Vert_Ref.xlsx"
path_fishbase_tax = "../../Metabarcoding Lab Resources/Reference Databases/taxonomic_classification_fishbase.csv"
path_mitofish_tax = "../../Metabarcoding Lab Resources/Reference Databases/taxonomic_classification_mitofish.csv"

## BLAST results
path_blast_gmgi = "../Taxonomic_assignment/BLASTResults_GMGI.txt"
path_blast_mito = "../Taxonomic_assignment/BLASTResults_Mito.txt"
path_blast_ncbi_taxassigned = "../Taxonomic_assignment/NCBI_taxassigned.txt"
path_blast_ncbi = "../Taxonomic_assignment/BLASTResults_NCBI.txt"

## ASV table results 
## confirm that the ASV_table.len.tsv name is correct for user's project
path_asv_table = "../ASV_table.len.tsv"
path_output_summary = "../overall_summary.tsv"

# output paths 
path_choice_required = "../Taxonomic_assignment/Choice_required_GMGI_multiplehits.xlsx"
path_disagree_list = "../Taxonomic_assignment/SampleReport_taxonomic_ID.xlsx"

results_rawreads_matrix = "../Results_rawreads_matrix.xlsx"
results_rawreads_long = "../Results_rawreads_long.xlsx"
```

## Load project metadata 

Metadata specific to each project. This contains information about each sample (e.g., month, site, time, sample type, etc.). Confirm that sample IDs match those used in the ASV_table.len.tsv file. 

```{r}
### User edits:
### 1. change path of metadata file

meta <- read.csv("../metadata/SBNMS_metadata.csv", header=TRUE) %>%
  mutate(sampleID = gsub("-", "_", sampleID))
## add code to manipulate sample ID if needed
## change samplesheet back to metadata.csv

meta_merged <- meta %>% 
  group_by(Site, Section, Substrate, SampleType) %>%
  mutate(sampleID = gsub("a$|b$|c$", "_sediment", sampleID)) %>% ungroup() %>% distinct()
  
```

## Load database metadata

No user edits in this section because paths have already been set above.

Warning note from phylo class

```{r}
# Load GMGI database information (common name, species name, etc.)
gmgi_db <- read_xlsx(path_GMGIdb, sheet = 1) %>% dplyr::rename(sseqid = Ref) %>%
  ## removing > from beginning of entires within Ref column
  mutate(sseqid = gsub(">", "", sseqid))

# Create a variable that defines taxonomic assignment levels
phylo_classifications = c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "species")

# Load taxonomic assignment information from fishbase and mitofish
tax_fishbase <- read.csv(path_fishbase_tax, header=T, col.names = c("Phylo", "Species_name")) %>%
   ## creating taxonomic assignment columns
  separate(Phylo, phylo_classifications, sep = ";", remove=T)

tax_mito <- read.csv(path_mitofish_tax, header=T, col.names = c("Species_name", "Phylo")) %>%
   ## creating taxonomic assignment columns
  separate(Phylo, phylo_classifications, sep = ";", remove=T)
```

# BLAST data input 

No user edits unless user changed blastn parameters from fisheries team default.

```{r}
## Setting column header names and classes
blast_col_headers = c("ASV_ID", "sseqid", "pident", "length", "mismatch", "gapopen",
                                        "qstart", "qend", "sstart", "send", "evalue", "bitscore")
blast_col_classes = c(rep("character", 2), rep("numeric", 10))
```

## GMGI database

No user edits.

```{r}
Blast_GMGI <- read.table(path_blast_gmgi, header=F, col.names = blast_col_headers, colClasses = blast_col_classes) %>%
  ## blast changes spaces to hyphons so we need to change that back to match our metadata
  mutate(sseqid = gsub("-", " ", sseqid)) %>%
  ## join with GMGI database information
  left_join(., gmgi_db, by = "sseqid")

## Check how many ASVs were identified with the GMGI Database
length(unique(Blast_GMGI$ASV_ID)) ## 142 ASVs 
```

## Mitofish database 

No user edits.

```{r}
Blast_Mito <- read.table(path_blast_mito, header=F, col.names = blast_col_headers, colClasses = blast_col_classes) %>%
  # renaming sseqid to species name
  dplyr::rename(Species_name = sseqid) %>%
  
  # replacing _ with spaces
  mutate(Species_name = gsub("_", " ", Species_name))

## Check how many ASVs were identified with the Mitofish Database
length(unique(Blast_Mito$ASV_ID)) ## 37 ASVs 
```


## NCBI database 

No user edits.

```{r}
NCBI_taxassigned <- read.delim2(path_blast_ncbi_taxassigned, header=F, col.names = c("staxid", "Phylo")) %>%
  ## creating taxonomic assignment columns
  separate(Phylo, c("Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species_name"), sep = ";") %>%
  ## creating species column based on Species_name
  mutate(., species = str_after_nth(Species_name, " ", 1))

Blast_NCBI <- read.table(path_blast_ncbi, header=F,
                           col.names = c("ASV_ID", "sseqid", "sscinames", "staxid", "pident", "length", "mismatch",
                                         "gapopen", "qstart", "qend", "sstart", "send", "evalue", "bitscore"),
                           colClasses = c(rep("character", 3), "integer", rep("numeric", 9))) %>%
  left_join(., NCBI_taxassigned, by = "staxid")

## Check how many ASVs were identified with the NCBI Database
length(unique(Blast_NCBI$ASV_ID)) ## 78 ASVs 
```


# Load DADA2 ASV Table 

The column headers will be the Sample IDs and the first column is the ASV ID. ASVs are given a "rank" based on sum of reads from that ASV (pre-filtering). 'Random' indicates that if ASVs are tied, then the code will randomly assign a rank for those tied. Because we don't need an exact rank here, 'random' will do for a tie-breaker.

No user edits.

```{r}
ASV_table_raw <- read_tsv(path_asv_table, show_col_types = FALSE) %>%
  ## calculate the sum of all reads for each ASV
  mutate(., ASV_sum = rowSums(across(where(is.numeric)))) %>% 
  
  ## calculate a ranking based on those sum calculated above
  mutate(ASV_rank = rank(-ASV_sum, ties.method='random')) %>%
  
  ## move the sum and rank columns to after ASV_ID and arrange by rank
  relocate(c(ASV_sum,ASV_rank), .after = ASV_ID) %>% arrange((ASV_rank)) 


### Stellwagen 2021 
### collapsing sediment samples 
ASV_table <- ASV_table_raw %>% gather("sampleID", "reads", c(C1_bottom:Sed_Neg2)) %>%
  left_join(., meta, by = "sampleID") %>%
  group_by(Site, Section, Substrate, SampleType, ASV_ID) %>%
  mutate(group_reads = sum(reads),
         sampleID = gsub("a$|b$|c$", "_sediment", sampleID)) %>% ungroup() %>%
  dplyr::select(-reads, -Site, -Section, -Substrate, -SampleType) %>% distinct() %>%
  spread(sampleID, group_reads)


## creating list of rankings
ASV_rank_list <- ASV_table %>% dplyr::select(ASV_ID, ASV_sum, ASV_rank)
```

# Taxonomic Assignment

Identifying where NCBI, Mito, and GMGI disagree on tax assignment. With the hierarchial approach, ASVs that match to GMGI and several other databases will only result in GMGI assignment. By reviewing this df, we can be sure we aren't missing an assignment in our GMGI curated database. 

**Sub-workflow:**  
1. Identify any ASVs that contain multiple hits within the GMGI database.
2. Identify entries that mismatch between GMGI, Mitofish, and NCBI databases.
3. Assign taxonomy based on hierarchical approach.
4. Edit taxonomy annotations based on mismatch table.  
5. Adjusting common name for those entries that don't have one (from Mito or GMGI). 

## Identify any ASVs that contain multiple hits within the GMGI database

At this point, a fisheries team member needs to make choices about which taxonomic assignment to accept.

#### Create list of those ASVs with multiple hits

No user edits.

```{r}
multiple_hit_choice <- Blast_GMGI %>% group_by(ASV_ID) %>%
  ## take top percent identity hit, count the number of top hits, and filter to those with more than 1 top hit 
  slice_max(pident, n=1) %>% count() %>% filter(n>1) %>%
  
  ## adding BLAST_GMGI information with these ASVs and ASV rank and sum
  left_join(., Blast_GMGI, by = "ASV_ID") %>%
  left_join(., ASV_rank_list, by = "ASV_ID") %>%
  
  ## moving database percent ID to be next to Blast percent ID
  relocate(c(db_percent_ID, ASV_sum, ASV_rank), .after = pident); multiple_hit_choice

## export this data frame as excel sheet 
multiple_hit_choice %>% write_xlsx(path_choice_required)
```

Based on the output above, user needs to make some choices.

#### Choosing one of several hits. 

Insert choice sheet for columns with x? instead of manually

```{r}
### User edits:
### 1. Add filtering cases using the format ASV_ID == "" ~ sseqid == ""
### example: ASV_ID == "1535a44c66f8850e6d30284f8ddeb38d" ~ sseqid == "3.00_Human_mito1"
### Keep the TRUE ~ TRUE at the end

Blast_GMGI_edited <- Blast_GMGI %>% 
  ### picking one of several hits
  filter(case_when(
    ASV_ID == "01fddebb1fe784a669f47c356f1e788b" ~ sseqid == "1.00_Winter_or_Yellowtail_flounder_Pseudopleuronectes_americanus_or_Pleuronectes_ferrugineus",
    ASV_ID == "1535a44c66f8850e6d30284f8ddeb38d" ~ sseqid == "3.00_Human_mito1",
    ASV_ID == "2a485cd03741c6fe6b14da2f20e691ff" ~ sseqid == "3.00_Human_mito1",
    ASV_ID == "5402cf89efb964e51543eeb9c0ddda4e" ~ sseqid == "3.50_Human_chromo17_RP1113L8b",
    ASV_ID == "7950b1078efc076defba9c936b970ef7" ~ sseqid == "3.50_Human_chromo17_RP1113L8",
    ASV_ID == "97692e77675cee377312fb71ecc51b4e" ~ sseqid == "2.00_Great Shearwater_Ardenna gravis",
    ASV_ID == "f47defcff9bda5faa019e12adffe30ef" ~ sseqid == "1.00_Winter_or_Yellowtail_flounder_Pseudopleuronectes_americanus_or_Pleuronectes_ferrugineus",
    TRUE ~ TRUE))
```

#### Confirming that all entries have been dealth with

No user edits.

```{r}
### Check the below output to confirm the filtering steps above worked (if it worked, it won't be in output)
Blast_GMGI_edited %>% group_by(ASV_ID) %>% slice_max(pident, n=1) %>% count() %>% filter(n>1)
```


## Identify entries that mismatch between GMGI, Mitofish, and NCBI databases

Creating a df called "Disagree". Review the output before moving onto the next section.

No user edits.

```{r}
Disagree <- Blast_GMGI_edited %>% group_by(ASV_ID) %>% 
  dplyr::rename(., GMGI_db_ID = db_percent_ID, GMGI_pident = pident) %>%
  ## Creating new columns with species name based on pident information
  mutate(
    GMGI_100 = if_else(GMGI_pident == 100, Species_name, NA_character_),
    GMGI_lessthan100 = if_else(GMGI_pident < 100, Species_name, NA_character_)) %>%
  
  ## taking only the top hit per ASV ID
  slice_max(GMGI_pident, n = 1, with_ties = FALSE) %>% ungroup() %>%

  ## filtering to distinct rows with selected columns
  distinct(ASV_ID, GMGI_db_ID, GMGI_pident, GMGI_100, GMGI_lessthan100) %>%
  
  ## adding Mitofish and editing the Blast_Mito df in the process
  full_join(Blast_Mito %>% dplyr::select(ASV_ID, Species_name) %>%
              dplyr::rename(Mitofish = Species_name) %>%
              distinct() %>% group_by(ASV_ID) %>%
              mutate(Mitofish = paste0(Mitofish, collapse = ";")),
            by = "ASV_ID") %>%
  
  ## adding NCBI and editing the Blast_NCBI df in the process
  full_join(Blast_NCBI %>% dplyr::select(ASV_ID, Species_name) %>%
              dplyr::rename(NCBI = Species_name) %>%
              distinct() %>% group_by(ASV_ID) %>%
              mutate(NCBI = paste0(NCBI, collapse = ";")),
            by = "ASV_ID") %>%
  
  ## adding ASV rank and sum information
  left_join(., ASV_rank_list, by = "ASV_ID") %>%

  ## filtering out duplicate rows
  distinct() %>%
  
  ## filtering to those entries that mismatch between GMGI, Mitofish, and NCBI
  filter(!(GMGI_100 %in% GMGI_lessthan100 | GMGI_100 %in% Mitofish | GMGI_100 %in% NCBI))

## export this data frame as excel sheet 
Disagree %>% write_xlsx(path_disagree_list)
```

## Assign taxonomy based on hierarchical approach

Taxonomic identification is taken from GMGI 100%, then GMGI <100%, then Mitofish 100%, and finally NCBI 100%.

No user edits.

```{r}
ASV_table_taxID <- ASV_table %>% 
  
  ## 1. Top hit from GMGI's database
  left_join(Blast_GMGI_edited %>% group_by(ASV_ID) %>%
              slice_max(pident, n = 1) %>%
                            dplyr::select(ASV_ID, Species_name),
            by = join_by(ASV_ID)) %>%
  
  ## 2. Mitofish database
  ### join df, select ASV_ID and Species_name columns, rename Species_name to Mito, call only distinct rows
  left_join(., Blast_Mito %>% dplyr::select(ASV_ID, Species_name) %>% dplyr::rename(Mito = Species_name) %>% distinct() %>%
              
              ### group by ASV_ID, and collapse all species names separated by ;, then take only distinct rows
              group_by(ASV_ID) %>% mutate(Mito = paste0(Mito, collapse = ";")) %>% distinct(), by = "ASV_ID") %>%
  
  ### if GMGI annotation is NA, then replace with Mitofish 
  mutate(., Species_name = ifelse(is.na(Species_name), Mito, Species_name)) %>%

  ## 3. NCBI database; same functions as above
  left_join(., Blast_NCBI %>% dplyr::select(ASV_ID, Species_name) %>% dplyr::rename(NCBI = Species_name) %>% distinct() %>%
              group_by(ASV_ID) %>% mutate(NCBI = paste0(NCBI, collapse = ";")) %>% distinct(), by = "ASV_ID") %>%
  mutate(., Species_name = ifelse(is.na(Species_name), NCBI, Species_name)) %>%
  
  ## 4. if Species name is STILL not filled, call it "unassigned"
  mutate(., Species_name = ifelse(is.na(Species_name), "unassigned", Species_name)) %>%  

  ## removing Mito spp and NCBI spp
  dplyr::select(-Mito, -NCBI) %>%
  
  ## move species name to be after ASV_ID
  relocate(., c(Species_name), .after = ASV_ID)
```

## Edit taxonomy annotations based on mismatch table

Override any annotations:

```{r}
### one more decision to make - shearwater species
## ASV = abb58e582fcc5bd9d2526b4bf98ed7a3
# Blast_GMGI_edited %>% subset(ASV_ID == "abb58e582fcc5bd9d2526b4bf98ed7a3") %>%
#   write_xlsx("../Taxonomic_assignment/Shearwater_choice.xlsx")

### User edits:
### 1. Add mutate cases using the format ASV_ID == "" ~ ""
### example: ASV_ID == "abb58e582fcc5bd9d2526b4bf98ed7a3" ~ "Ardenna griseus or Ardenna gravis",
### Keep the TRUE ~ Species_name at the end

### 2. Add ifelse() cases using the format ifelse(grepl('', Species_name), "", Species_name
### example: ifelse(grepl('Homo sapiens', Species_name), "Homo sapiens", Species_name
### example: ifelse(grepl('Phyllozelus siccus', Species_name), "unassigned", Species_name)

ASV_table_taxID <- ASV_table_taxID %>%
  ## Use mutate case_when() for specific ASV IDs
  mutate(Species_name = case_when(
    ASV_ID == "abb58e582fcc5bd9d2526b4bf98ed7a3" ~ "Ardenna gravis",
    TRUE ~ Species_name)) %>%

  ## OR Use ifelse() function to find entries with specific content that might apply to mulitple ASVs
  mutate(Species_name = ifelse(grepl('eukaryotic', Species_name), "unassigned", Species_name),
         Species_name = ifelse(grepl('MT-2021', Species_name), "unassigned", Species_name),
         Species_name = ifelse(grepl('Homo sapiens', Species_name), "Homo sapiens", Species_name))

```

### Confirm all entries are dealt with

No user edits.

```{r}
## Output will be blank
ASV_table_taxID %>% dplyr::select(Species_name) %>% distinct() %>% 
  filter(., grepl(";", Species_name)) %>% arrange(Species_name) 
```

## Adjusting common name for those entries that don't have one (from Mito or NCBI)

No user edits.

```{r}
ASV_table_taxID %>% subset(Species_name == "unassigned") %>%
  summarise(sum = sum(ASV_sum))

### add common name column to df
ASV_table_taxID <- ASV_table_taxID %>%
  left_join(., gmgi_db %>% dplyr::select(Species_name, Common_name, Category) %>% distinct(), by = "Species_name") %>%
  relocate(., c(Common_name, Category), .after = Species_name)

### print entries with no common name
ASV_table_taxID %>% dplyr::select(Species_name, Common_name) %>% filter(is.na(Common_name)) %>% distinct()
```

Editing common names and category when needed.

```{r}
### User edits:
### 1. Add mutate cases using the format ifelse(grepl('', Species_name), "", Common_name
### example: ifelse(grepl('unassigned', Species_name), "unassigned", Common_name)
### 2. Add mutate cases using the format ifelse(grepl('', Species_name), "", Category

ASV_table_taxID <- ASV_table_taxID %>% 
  # changing specific entries for Common name
  mutate(Common_name = ifelse(grepl('unassigned', Species_name), "unassigned", Common_name)
         ) %>%
  
  # changing specific entries for category
  mutate(Category = ifelse(grepl('unassigned', Species_name), "unassigned", Category)
         )

## printing list of species name without common names 
## after additions to mutate function above, this output should be zero 
ASV_table_taxID %>% dplyr::select(Species_name, Common_name) %>% filter(is.na(Common_name)) %>% distinct()
```

# Filtering: Filter ASV by less than 0.1% reads and then collapse by group

## Filter out reads that are less than 0.1% of ASV (row) total per sample. 

Create an output of what you're losing with filtering
Can sumVar be ASV_sum

```{r}
### User edits:
### 1. In mutate(sumVar = ), change FIRST_SAMPLE:LAST_SAMPLE to sample 1 column and the last sample column 
### 2. In mutate(across(.cols = )), change FIRST_SAMPLE:LAST_SAMPLE to sample 1 column and the last sample column
### example: C1_bottom:Sed_Neg2

ASV_table_taxID_filtered <- ASV_table_taxID %>%
  ## telling the df we are doing the following function by rows (ASVs)
  rowwise() %>%
  
  ## calculating rowSum (total reads per ASV)
  mutate(sumVar = sum(c_across(7:110))) %>% relocate(., sumVar, .after = Species_name) %>%
  
  ## filtering out any values that are less than 0.001 of the total ASV read # in each sample
  mutate(across(.cols = (7:110),
                .fns = ~ ifelse((.x/sumVar)<0.001, NA, .x))) %>% dplyr::select(-sumVar) %>% ungroup()
```


# Collapsing read counts by species name

```{r}
### User edits:
### 1. In mutate(sumVar = ), change FIRST_SAMPLE:LAST_SAMPLE to sample 1 column and the last sample column 
### example: C1_bottom:Sed_Neg2

ASV_table_taxID_collapsed <- ASV_table_taxID_filtered %>% 
  # removing original ASV_ID to collapse
  dplyr::select(-ASV_ID) %>%  
  
  ## group by Species_name and sample
  group_by(Species_name, Common_name, Category) %>%
  
  ## sum down column by species name and sample to collapse
  summarise(across(c(C1_bottom:Sed_Neg2), ~ sum(., na.rm = TRUE)))

```


# Creating results output 

Raw reads

```{r}
## Raw reads matrix (wide format)
ASV_table_taxID_collapsed %>% write_xlsx(results_rawreads_matrix)

### User edits:
### 1. In gather("sampleID", "reads", ..), change FIRST_SAMPLE:LAST_SAMPLE to sample 1 column and the last sample column 
### example: C1_bottom:Sed_Neg2

## Raw reads long format and filtering out entries with zero reads
ASV_table_taxID_collapsed %>% 
  gather("sampleID", "reads", c(C1_bottom:Sed_Neg2)) %>%
  filter(reads > 0) %>% write_xlsx(results_rawreads_long)
```

Relative Abundance

make_relative() requires sites in rows and species in columns

```{r}
matrix_df <- ASV_table_taxID_collapsed %>% ungroup() %>% 
  dplyr::select(-Common_name, -Category) %>% 
  gather("sampleID", "relab", 2:last_col()) %>%
  spread(Species_name, relab) %>%
  column_to_rownames(., var = "sampleID")

## Creating matrix
data.matrix <- as.matrix(matrix_df)

## Calculating relative abundance
data_relativeab_matrix <- make_relative(data.matrix)

## Transforming df with common name, category info 
data_relativeab_df <- as.data.frame(data_relativeab_matrix) %>% rownames_to_column(var = "sampleID") %>%
  right_join(meta_merged, ., by = "sampleID") 

data_relativeab_df %>% write_xlsx("Results_relab_matrix.xlsx")

data_relativeab_df %>% 
  gather("Species_name", "relab", c(6:last_col())) %>% 
  left_join(., ASV_table_taxID_collapsed %>% dplyr::select(Species_name, Common_name, Category) %>% distinct(), 
            by = "Species_name") %>%
  write_xlsx("Results_relab_long.xlsx")
```

## Manuscript stats 


```{r}
## number of ASVs 
nrow(ASV_table_taxID_filtered)
## number of assigned ASVs 
nrow(ASV_table_taxID_filtered %>% subset(!Species_name == "unassigned"))
## number of ASVs that were human, livestock, unassigned
nrow(ASV_table_taxID_filtered %>% subset(Category == "unassigned" | Category == "Human" |
                                           Category == "Livestock"))

## number of ASVs that were fish
nrow(ASV_table_taxID_filtered %>% subset(Category == "Teleost Fish"))
nrow(ASV_table_taxID_filtered %>% subset(Category == "Marine Mammal"))
nrow(ASV_table_taxID_filtered %>% subset(Category == "Bird"))

ASV_table_taxID_collapsed %>% 
  gather("sampleID", "reads", c(C1_bottom:Sed_Neg2)) %>%
  group_by(Category) %>%
  summarise(sum = sum(reads)) %>% ungroup() %>%
  mutate(total = sum(sum),
         percent = sum/total*100)

ASV_table_taxID_collapsed %>% 
  gather("sampleID", "reads", c(C1_bottom:Sed_Neg2)) %>%
  group_by(Species_name, Common_name) %>%
  subset(!Category == "Human" & !Category == "Livestock" & !Category == "unassigned") %>%
  summarise(sum = sum(reads)) %>% ungroup() %>%
  mutate(total = sum(sum),
         percent = sum/total*100) %>%
  arrange(desc(percent))

## adding average relative abundance values 
data_relativeab_df %>% 
  gather("Species_name", "relab", 6:46) %>% 
  group_by(Species_name) %>% 
  filter(!is.na(relab)) %>% 
  summarise(
    mean_relab = mean(relab),
    se_relab = sd(relab) / sqrt(n())
  ) %>% 
  mutate(
    mean_relab = round(mean_relab, 4) * 100,
    se_relab = round(se_relab, 4) * 100
  ) %>%
  arrange(desc(mean_relab))
```


















